On exponential sums arising from the classical doubling method

### 2025-03-31 main.tex
Chaos. Replacing \alpha with \alpha^{-1} in the Gauss sum

% Matrices macros
\newcommand{\transpose}[1]{\, {}^{t}#1}
\newcommand{\inverseTranspose}[1]{#1^{\iota}}
\newcommand{\involution}[1]{#1^{c}}
\newcommand{\minusInvolution}[1]{#1^{-c}}
\newcommand{\involutionPlusOne}[1]{#1^{1+c}}
\newcommand{\IdentityMatrix}[1]{I_{#1}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\antidiag}{\operatorname{\mathrm{antidiag}}}
\newcommand{\trace}{\operatorname{tr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\SO}{\mathrm{SO}}
\newcommand{\GSO}{\mathrm{GSO}}
\newcommand{\Sp}{\mathrm{Sp}}
\newcommand{\GSp}{\mathrm{GSp}}
\newcommand{\UnitaryGroup}{\mathrm{U}}
\newcommand{\UnipotentSubgroup}{U}
\newcommand{\UnipotentRadical}{N}
\newcommand{\ParabolicSubgroup}{P}
\newcommand{\GroupExtension}[1]{\widetilde{#1}}

% Finite field macros
\newcommand{\FieldNorm}[2]{\mathrm{N}_{#1:#2}}
\newcommand{\aFieldNorm}{\mathrm{N}}
\newcommand{\finiteField}{\mathbb{F}}
\newcommand{\quadraticExtension}{\mathbb{E}}
\newcommand{\finiteFieldExtension}[1]{\finiteField_{#1}}
\newcommand{\quadraticFieldExtension}[1]{\quadraticExtension_{#1}}
\newcommand{\NormOneGroup}[1]{\finiteFieldExtension{#1}^{\aFieldNorm = 1}}
\newcommand{\algebraicClosure}[1]{\overline{#1}}
\newcommand{\Galois}{\operatorname{Gal}}
\newcommand{\Frobenius}{\operatorname{Fr}}
\newcommand{\restrictionOfScalars}[3]{\operatorname{Res}_{#1 \slash #2}{#3}}
\newcommand{\multiplcativeScheme}{\algebraicGroup{G}_m}
\newcommand{\affineLine}{\mathbb{A}^1}
\newcommand{\squareMatrix}{\operatorname{Mat}}
\newcommand{\Mat}[2]{\operatorname{Mat}_{#1 \times #2}}
\newcommand{\GaussSum}[2]{\mathcal{G}\left(#1, #2\right)}
\newcommand{\dblJacobiSum}[2]{\mathcal{J}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\posDblJacobiSum}[2]{\mathcal{J}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\negDblJacobiSum}[2]{\mathcal{J}_{-}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\JacobiKernel}[1]{\Phi_{#1}}
\newcommand{\posJacobiKernel}[1]{\Phi^{+}_{#1}}
\newcommand{\negJacobiKernel}[1]{\Phi^{-}_{#1}}
\newcommand{\genJacobiKernel}[1]{\Phi^{\pm}_{#1}}
\newcommand{\genHermitianJacobiKernel}[2]{\Phi^{\pm}_{#1,#2}}

@@

Let $\finiteField$ be a finite field with $q$ elements and let $\fieldCharacter \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character. Given a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ the normalized Gauss sum corresponding to the data $\left(\chi, \fieldCharacter\right)$ is defined by the formula
$$\tau\left(\chi, \fieldCharacter\right) = -\frac{1}{\sqrt{q}}\sum_{x \in \multiplicativegroup{\finiteField}} \chi\left(x\right) \fieldCharacter\left(x\right).$$

In the 1960s, Kondo \cite{Kondo1963} introduced an interesting exponential sum, which can be thought of as a higher dimensional version of the Gauss sum defined above. Let $\pi$ be an irreducible representation of $\GL_n\left(\finiteField\right)$. Then the sum $$\GaussSum{\pi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \fieldCharacter\left(\trace g\right) \pi\left(g\right)$$
defines an operator in $\Hom_{\GL_n\left(\finiteField\right)}\left(\pi, \pi\right)$. Since $\pi$ is irreducible, by Schur's lemma there exists a scalar $\GaussSumScalar{\pi}{\fieldCharacter} \in \cComplex$ such that $$\GaussSum{\pi}{\fieldCharacter} = \GaussSumScalar{\pi}{\fieldCharacter} \cdot \idmap_{\pi}.$$

@@

Let $\tau$ be an irreducible representation of $\GL_n\left(\finiteField\right)$. 
For a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, denote the \emph{twisted Gauss sum}
$$\GaussSum{\tau \times \chi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \chi\left(\det g\right) \fieldCharacter\left(\trace g\right).$$
This element lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$ and therefore by Schur's lemma there exists a complex number $\GaussSumScalar{\tau \times \chi}{\fieldCharacter} \in \cComplex$ such that
$$\GaussSum{\tau \times \chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi}{\fieldCharacter} \cdot \idmap_\tau.$$ The computation of this scalar is known due to Kondo \cite{Kondo1963}.

@@

If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \fieldCharacter_n\left(x\right),$$where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$. If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote the \emph{twisted Gauss sum}
$$\tau\left(\alpha \times \chi, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha\left(x\right) \chi\left( \FieldNorm{n}{1}\left(x\right)\right) \fieldCharacter_n\left(x\right).$$

@@

\begin{proposition}\label{prop:doubling-for-gln-in-terms-of-kondo}
	We have the identity
	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
			y^{-1} x = g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
\end{proposition}
\begin{proof}
	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g+\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
	By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $X \in \GL_k\left(\finiteField\right)$. Thus	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g+\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
	Changing variables $h \mapsto X^{-1} h$, we get
	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(Xg\right)\right) \fieldCharacter\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter\left(\trace X\right).$$
	Changing variables again $h \mapsto -h$ and setting $Xg = x$ and $X = y$, we get  
	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
			y^{-1} x = g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
\end{proof}

We now use this to compute $\posDblJacobiSum{\tau}{\chi}$. We have that $$\posDblJacobiSum{\tau}{\chi} = q^{-k^2} \chi\left(-1\right)^k \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \tau\left(y^{-1} x\right).$$
The last equality implies the following result.
\begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
	$$\posDblJacobiSumScalar{\tau}{\chi} = \chi\left(-1\right)^k \GaussSumScalar{\chi}{\fieldCharacter}^k \GaussSumScalar{\tau}{\fieldCharacter} \GaussSumScalar{\tau^{\vee} \times \chi^{-1}}{\fieldCharacter}.$$
\end{theorem}

@@

\begin{theorem}\label{thm:multiplicativity-in-terms-of-gauss-sums}
	Let $\pi'$ be an irreducible representation of $H'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\quadraticExtension\right)$. Then for any irreducible representation $\pi$ of $H$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{H}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\involutionPlusOne{\chi} \ne 1$, we have
	$$\dblJacobiSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(\pm 1\right) \chi\left(\pm 1\right)^k \GaussSumScalar{\involutionPlusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}^k \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter_{\quadraticExtension}} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter_{\quadraticExtension}} \dblJacobiSumScalar{\pi'}{\chi}.$$
\end{theorem}

@@

We define a normalization factor as follows $$c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) = \begin{dcases}
	\tau\left(\chi^2, \fieldCharacter\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is even,}\\
	\chi\left(2\right) \tau\left(\chi^2, \fieldCharacter\right)^{\frac{\dim_{\finiteField} \hermitianSpace - 1}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is odd,}	\\
	\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \quadraticExtension \ne \finiteField.
\end{dcases}$$
Notice that if $\quadraticExtension \ne \finiteField$ then by the Hasse--Davenport relation $\tau\left(\chi\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{2} = \tau\left(\involutionPlusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)$.

For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \minusInvolution{\chi}}{\fieldCharacter} \GaussSumScalar{\Contragradient{\tau} \times \chi^{-1}}{\fieldCharacter}.$$
For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \frac{\posDblJacobiSumScalar{\pi}{\chi}}{c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)}.$$
Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.

@@

\begin{remark}
	The ``correct'' gamma factor (expected by Langlands functoriality) is given by $$\dblLanglandsGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} \cdot \begin{dcases}
				\left(-1\right)^n & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = 1\\
				\left(-1\right)^{n+1} \tau\left(\chi^{-1}, \fieldCharacter\right) & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = -1 \\
				1 & \text{otherwise.}
	\end{dcases},$$
	where $n = \left\lfloor \frac{\dim_{\finiteField} \hermitianSpace}{2} \right\rfloor$.
	However, we will not need this version for our purposes. \elad{Check odd orthogonal case. Probably needs a sign modification (the formula needs to be $\left(-1\right)^{\text{dual group dimension}} \times \text{product of Gauss sums}$). $\varepsilon_{\algebraicGroup{G}}$ contributes half of the dimension so that's why we add another half here.}
\end{remark}

@@

\begin{theorem}\label{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $H$. Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$. Denote \begin{align*}
		g_T\left(\chi, \theta, \fieldCharacter\right)
		= & \prod_{i=1}^s \GaussSumCharacter{\left(\theta'_i\right)^{-1}}{\chi^{-1}}{\fieldCharacter_{2m_i}} \cdot \prod_{j=1}^r \GaussSumCharacter{\involution{\alpha_j}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}} \GaussSumCharacter{\alpha_j^{-1}}{\chi^{-1}}{\fieldCharacter_{\quadraticFieldExtension{k_j}}}.
	\end{align*} Then
	\begin{align*}
		 \dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \varepsilon_{\algebraicGroup{H}} R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right),
	\end{align*}
	and \begin{align*}
		\dblNegVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \begin{dcases}
			0 & \dim_{\finiteField} \hermitianSpace \text{ is odd.}\\
			\dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} \cdot \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right) & \text{ otherwise.}
		\end{dcases}
	\end{align*}
\end{theorem}
\begin{proof}
	Notice that if $\dim_{\finiteField} \hermitianSpace$ is odd then $\negJacobiKernel{\chi}\left(t\right) = 0$ for any $t \in T$, as $\idmap_{\hermitianSpace} - t$ always has determinant zero.

>>>>

% Matrices macros
\newcommand{\transpose}[1]{\, {}^{t}#1}
\newcommand{\inverseTranspose}[1]{#1^{\iota}}
\newcommand{\involution}[1]{#1^{c}}
\newcommand{\minusInvolution}[1]{#1^{-c}}
\newcommand{\involutionPlusOne}[1]{#1^{1+c}}
\newcommand{\minusInvolutionMinusOne}[1]{#1^{-1-c}}
\newcommand{\IdentityMatrix}[1]{I_{#1}}
\newcommand{\diag}{\mathrm{diag}}
\newcommand{\antidiag}{\operatorname{\mathrm{antidiag}}}
\newcommand{\trace}{\operatorname{tr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\SO}{\mathrm{SO}}
\newcommand{\GSO}{\mathrm{GSO}}
\newcommand{\Sp}{\mathrm{Sp}}
\newcommand{\GSp}{\mathrm{GSp}}
\newcommand{\UnitaryGroup}{\mathrm{U}}
\newcommand{\UnipotentSubgroup}{U}
\newcommand{\UnipotentRadical}{N}
\newcommand{\ParabolicSubgroup}{P}
\newcommand{\GroupExtension}[1]{\widetilde{#1}}

% Finite field macros
\newcommand{\FieldNorm}[2]{\mathrm{N}_{#1:#2}}
\newcommand{\aFieldNorm}{\mathrm{N}}
\newcommand{\finiteField}{\mathbb{F}}
\newcommand{\quadraticExtension}{\mathbb{E}}
\newcommand{\finiteFieldExtension}[1]{\finiteField_{#1}}
\newcommand{\quadraticFieldExtension}[1]{\quadraticExtension_{#1}}
\newcommand{\NormOneGroup}[1]{\finiteFieldExtension{#1}^{\aFieldNorm = 1}}
\newcommand{\algebraicClosure}[1]{\overline{#1}}
\newcommand{\Galois}{\operatorname{Gal}}
\newcommand{\Frobenius}{\operatorname{Fr}}
\newcommand{\restrictionOfScalars}[3]{\operatorname{Res}_{#1 \slash #2}{#3}}
\newcommand{\multiplcativeScheme}{\algebraicGroup{G}_m}
\newcommand{\affineLine}{\mathbb{A}^1}
\newcommand{\squareMatrix}{\operatorname{Mat}}
\newcommand{\Mat}[2]{\operatorname{Mat}_{#1 \times #2}}
\newcommand{\GaussSum}[2]{\mathcal{G}\left(#1, #2\right)}
\newcommand{\GaussSumSingleCharacter}[2]{\tau\left(#1, #2\right)}
\newcommand{\dblJacobiSum}[2]{\mathcal{J}_{\pm}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\posDblJacobiSum}[2]{\mathcal{J}_{+}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\negDblJacobiSum}[2]{\mathcal{J}_{-}^{\mathrm{dbl}}\left(#1, #2\right)}
\newcommand{\JacobiKernel}[1]{\Phi_{#1}}
\newcommand{\posJacobiKernel}[1]{\Phi^{+}_{#1}}
\newcommand{\negJacobiKernel}[1]{\Phi^{-}_{#1}}
\newcommand{\genJacobiKernel}[1]{\Phi^{\pm}_{#1}}
\newcommand{\genHermitianJacobiKernel}[2]{\Phi^{\pm}_{#1,#2}}

@@

Let $\finiteField$ be a finite field with $q$ elements and let $\fieldCharacter \colon \finiteField \to \multiplicativegroup{\cComplex}$ be a non-trivial character. Given a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ the normalized Gauss sum corresponding to the data $\left(\chi, \fieldCharacter\right)$ is defined by the formula
$$\tau\left(\chi, \fieldCharacter\right) = -\frac{1}{\sqrt{q}}\sum_{x \in \multiplicativegroup{\finiteField}} \chi^{-1}\left(x\right) \fieldCharacter\left(x\right).$$

In the 1960s, Kondo \cite{Kondo1963} introduced an interesting exponential sum, which can be thought of as a higher dimensional version of the Gauss sum defined above. Let $\pi$ be an irreducible representation of $\GL_n\left(\finiteField\right)$. Then the sum $$\GaussSum{\pi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \fieldCharacter\left(\trace g^{-1}\right) \pi\left(g\right)$$
defines an operator in $\Hom_{\GL_n\left(\finiteField\right)}\left(\pi, \pi\right)$. Since $\pi$ is irreducible, by Schur's lemma there exists a scalar $\GaussSumScalar{\pi}{\fieldCharacter} \in \cComplex$ such that $$\GaussSum{\pi}{\fieldCharacter} = \GaussSumScalar{\pi}{\fieldCharacter} \cdot \idmap_{\pi}.$$

@@

Let $\tau$ be an irreducible representation of $\GL_n\left(\finiteField\right)$. 
For a character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, denote the \emph{twisted Gauss sum}
$$\GaussSum{\tau \times \chi}{\fieldCharacter} = q^{-\frac{n^2}{2}} \sum_{g \in \GL_n\left(\finiteField\right)} \tau\left(g\right) \chi\left(\det g\right) \fieldCharacter\left(\trace g^{-1}\right).$$
This element lies in $\Hom_{\GL_n\left(\finiteField\right)}\left(\tau, \tau\right)$ and therefore by Schur's lemma there exists a complex number $\GaussSumScalar{\tau \times \chi}{\fieldCharacter} \in \cComplex$ such that
$$\GaussSum{\tau \times \chi}{\fieldCharacter} = \GaussSumScalar{\tau \times \chi}{\fieldCharacter} \cdot \idmap_\tau.$$ The computation of this scalar is known due to Kondo \cite{Kondo1963}.

@@

If $\alpha \colon \multiplicativegroup{\finiteFieldExtension{n}} \to \multiplicativegroup{\cComplex}$ is a character, denote the \emph{Gauss sum} $$\tau\left(\alpha, \fieldCharacter_n\right) = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha^{-1}\left(x\right) \fieldCharacter_n\left(x\right),$$where $\fieldCharacter_n \colon \finiteFieldExtension{n} \to \multiplicativegroup{\cComplex}$ is given by $\fieldCharacter_n = \fieldCharacter \circ \trace_{\finiteFieldExtension{n} \slash \finiteField}$. If $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$ is a character and if $\alpha$ is as above, denote the \emph{twisted Gauss sum}
$$\GaussSumCharacter{\alpha}{\chi}{\fieldCharacter_n} = -q^{-\frac{n}{2}}\sum_{x \in \multiplicativegroup{\finiteFieldExtension{n}}} \alpha^{-1}\left(x\right) \chi^{-1}\left( \FieldNorm{n}{1}\left(x\right)\right) \fieldCharacter_n\left(x\right).$$

@@

\begin{proposition}\label{prop:doubling-for-gln-in-terms-of-kondo}
	We have the identity
	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi^{-1}_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
			y^{-1} x = g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
\end{proposition}
\begin{proof}
	We write $$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}}\sum_{X \in \squareMatrix_k\left(\finiteField\right)} \sum_{h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g+\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
	By \Cref{lem:sum-vanishes-for-singular-matrices}, we can reduce the sum to $X \in \GL_k\left(\finiteField\right)$. Thus	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(X\left(g+\IdentityMatrix{k}-h\right)\right)\right) \chi\left(\det h\right).$$
	Changing variables $h \mapsto X^{-1} h$, we get
	$$\Phi_{\chi}\left(g\right) = \frac{1}{\sizeof{\squareMatrix_k\left(\finiteField\right)}} \sum_{X, h \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace \left(Xg\right)\right) \fieldCharacter\left(-\trace h\right) \chi\left(\det h\right) \chi^{-1}\left(\det X\right) \fieldCharacter\left(\trace X\right).$$
	Changing variables again $h \mapsto -h$ and setting $Xg = x$ and $X = y$, we get  
	$$\Phi_{\chi}\left(g\right) = \chi\left(-1\right)^k q^{-\frac{k^2}{2}} \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{\substack{x, y \in \GL_k\left(\finiteField\right)\\
			y^{-1} x = g}} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right).$$
\end{proof}

We now use this to compute $\posDblJacobiSum{\tau}{\chi}$. We have that $$\posDblJacobiSum{\tau}{\chi} = q^{-k^2} \chi\left(-1\right)^k \GaussSumScalar{\chi_{\GL_k}}{\fieldCharacter} \sum_{x, y \in \GL_k\left(\finiteField\right)} \fieldCharacter\left(\trace x\right) \chi^{-1}\left(\det y\right) \fieldCharacter\left(\trace y\right) \tau\left(y^{-1} x\right).$$
The last equality implies the following result.
\begin{theorem}\label{thm:gln-doubling-gauss-sum-in-terms-of-kondo}For any irreducible representation $\tau$ of $\GL_k\left(\finiteField\right)$ and any non-trivial character $\chi \colon \multiplicativegroup{\finiteField} \to \multiplicativegroup{\cComplex}$, the following identity holds:
	$$\posDblJacobiSumScalar{\tau}{\chi} = \chi\left(-1\right)^k \left(-\tau\left(\chi^{-1},\fieldCharacter\right)\right)^k \GaussSumScalar{\tau^{\vee}}{\fieldCharacter} \GaussSumScalar{\tau \times \chi}{\fieldCharacter}.$$
\end{theorem}

@@

\begin{theorem}\label{thm:multiplicativity-in-terms-of-gauss-sums}
	Let $\pi'$ be an irreducible representation of $H'$ and let $\tau$ be an irreducible representation of $\GL_k\left(\quadraticExtension\right)$. Then for any irreducible representation $\pi$ of $H$ which appears as a subrepresentation the parabolic induction $\rho = \Ind{P}{H}{\tau \overline{\otimes} \pi'}$ and any $\chi$ such that $\involutionPlusOne{\chi} \ne 1$, we have
	$$\dblJacobiSumScalar{\pi}{\chi} = \centralCharacter{\tau}\left(\pm 1\right) \chi\left(\pm 1\right)^k \left(-\GaussSumSingleCharacter{\minusInvolutionMinusOne{\chi}}{\fieldCharacter_{\quadraticExtension}}\right)^k \GaussSumScalar{\involution{\left(\Contragradient{\tau}\right)} \times \chi}{\fieldCharacter_{\quadraticExtension}} \GaussSumScalar{\tau \times \chi}{\fieldCharacter_{\quadraticExtension}} \dblJacobiSumScalar{\pi'}{\chi}.$$
\end{theorem}

@@

We define a normalization factor as follows $$c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) = \begin{dcases}
	\tau\left(\chi^{-2}, \fieldCharacter\right)^{\frac{\dim_{\finiteField} \hermitianSpace}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is even,}\\
	\chi\left(2\right) \tau\left(\chi^{-2}, \fieldCharacter\right)^{\frac{\dim_{\finiteField} \hermitianSpace - 1}{2}} & \quadraticExtension = \finiteField,\,\, \dim_{\finiteField} \hermitianSpace \text{ is odd,}	\\
	\tau\left(\chi^{-1}\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{\dim_{\quadraticExtension} \hermitianSpace} & \quadraticExtension \ne \finiteField.
\end{dcases}$$
Notice that if $\quadraticExtension \ne \finiteField$ then by the Hasse--Davenport relation $\tau\left(\chi^{-1}\restriction_{\multiplicativegroup{\finiteField}}, \fieldCharacter\right)^{2} = \tau\left(\minusInvolutionMinusOne{\chi}, \fieldCharacter_{\quadraticExtension}\right)$.

For an irreducible representation  $\tau$ of $\GL_k\left(\quadraticExtension\right)$, define $$\dblGammaFactor{\tau}{\chi}{\fieldCharacter} = \GaussSumScalar{\Contragradient{\tau} \times \involution{\chi}}{\fieldCharacter} \GaussSumScalar{\tau \times \chi}{\fieldCharacter}.$$
For an irreducible representation $\pi$ of $G$, define the \emph{doubling method gamma factor} $$\dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \frac{\posDblJacobiSumScalar{\pi}{\chi}}{c_{\hermitianSpace}\left(\chi, \fieldCharacter\right)}.$$
Using this notation and using the multiplicativity property of Kondo's Gauss sum and \Cref{thm:multiplicativity-in-terms-of-gauss-sums}, we have the following multiplicativity property.

@@

\begin{remark}
	The ``correct'' gamma factor (expected by Langlands functoriality) is given by $$\dblLanglandsGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} = \dblGammaFactorSpace{\hermitianSpace}{\pi}{\chi}{\fieldCharacter} \cdot \begin{dcases}
				\left(-1\right)^n & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = 1\\
				\left(-1\right)^{n+1} \tau\left(\chi, \fieldCharacter\right) & \quadraticExtension = \finiteField \text{ and } \epsilon_{\hermitianSpace} = -1 \\
				1 & \text{otherwise.}
	\end{dcases},$$
	where $n = \left\lfloor \frac{\dim_{\finiteField} \hermitianSpace}{2} \right\rfloor$.
	However, we will not need this version for our purposes. \elad{Check odd orthogonal case. Probably needs a sign modification (the formula needs to be $\left(-1\right)^{\text{dual group dimension}} \times \text{product of Gauss sums}$). $\varepsilon_{\algebraicGroup{G}}$ contributes half of the dimension so that's why we add another half here.} \elad{Maybe this is the better version for Calvin's computations}
\end{remark}

@@

\begin{theorem}\label{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters}
	Suppose that $T \cong \prod_{j=1}^r \multiplicativegroup{\quadraticFieldExtension{k_j}} \times \prod_{i=1}^s \finiteFieldExtension{2m_i}^1$ is a maximal torus of $H$. Suppose that $\theta \colon T \to \multiplicativegroup{\cComplex}$ is a character and that under the above isomorphism $\theta = \alpha_1 \times \dots \times \alpha_r \times \theta_1 \times \dots \times \theta_s$, where $\alpha_j \colon \multiplicativegroup{\quadraticFieldExtension{k_j}} \to \multiplicativegroup{\cComplex}$ and $\theta_i \colon \finiteFieldExtension{2m_i}^1 \to \multiplicativegroup{\cComplex}$ are characters for every $i$ and $j$. Denote \begin{align*}
		g_T\left(\chi, \theta, \fieldCharacter\right)
		= & \prod_{i=1}^s \GaussSumCharacter{\theta'_i}{\chi}{\fieldCharacter_{2m_i}} \cdot \prod_{j=1}^r \GaussSumCharacter{\minusInvolution{\alpha_j}}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k_j}}} \GaussSumCharacter{\alpha_j}{\chi}{\fieldCharacter_{\quadraticFieldExtension{k_j}}}.
	\end{align*} Then
	\begin{align*}
		 \dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \varepsilon_{\algebraicGroup{H}} R_{T,\theta}\left(1\right) c_{\hermitianSpace}\left(\chi, \fieldCharacter\right) g_T\left(\chi, \theta, \fieldCharacter\right),
	\end{align*}
	and \begin{align*}
		\dblNegVirtualJacobiSumScalar{R_{T, \theta}}{\chi} = \begin{dcases}
			0 & \dim_{\finiteField} \hermitianSpace \text{ is odd.}\\
			\dblPosVirtualJacobiSumScalar{R_{T, \theta}}{\chi} \cdot \prod_{i=1}^s \theta_i\left(-1\right) \cdot \prod_{j=1}^r \alpha_j\left(-1\right) & \text{ otherwise.}
		\end{dcases}
	\end{align*}
\end{theorem}
\begin{proof}
	Notice that if $\dim_{\finiteField} \hermitianSpace$ is odd then $\negJacobiKernel{\chi}\left(t\right) = 0$ for any $t \in T$, as $\idmap_{\hermitianSpace} - t$ always has determinant zero.
